Follow-up Samples

### 2016-12-07 submission/manuscript_outline_20161024.Rmd
Figure legend updates

**Figure 1: Change in Thetayc and Fit between initial and follow up in adenoma or carcinoma group.**  A) No significant difference was found between the adenoma and carcinoma group for thetayc (P-value = `r format(change_summary['thetayc', 'Pvalue'], scientific = FALSE, digits = 3)`).  B) A significant difference was found between the adenoma and carcinoma group for Fit (P-value = `r format(change_summary['fit', 'Pvalue'], scientific = TRUE, digits = 3)`).

@@

**Figure 3: Graph of the Receiver Operating Characteristic Curve on Test Set Performance of the Best, Middle, and Worse Training Models.** For each of the 100 training cohort sets used had `r round(length(rownames(metaI))*0.8)` individuals and the testing cohort sets had `r round(length(rownames(good_metaf))*0.2)` individuals.  The AUC on the test sets for the best, middle, and worse models from training were `r format(model_test_AUC_summary["best", "AUC"], digits = 3)`, `r format(model_test_AUC_summary["middle", "AUC"], digits = 3)`, and `r format(model_test_AUC_summary["worse", "AUC"], digits = 3)`, respectively.  cvAUC is the 10-fold cross-validated AUC from training.

**Figure 4: Breakdown by Carcinoma and Adenoma of Prediction Results for Initial and Follow Up***  A) Positive probability adjustment of those with carcinoma from intial to follow up sample  B) Positive probability adjustment of those with adenoma as well as those with SRN and the probability adjustment from initial to follow up sample.  THe dotted line represents the threshold used to make the decision of whether a sample was lesion positive or not.

>>>>

**Figure 1: Change in Thetayc and Fit between initial and follow up in adenoma or carcinoma group.**  A) No significant difference was found between the adenoma and carcinoma group for thetayc (P-value = `r format(change_summary['thetayc', 'Pvalue'], scientific = FALSE, digits = 3)`).  B) A significant difference was found between the adenoma and carcinoma group for FIT (P-value = `r format(change_summary['fit', 'Pvalue'], scientific = TRUE, digits = 3)`).

@@

**Figure 3: Graph of the Receiver Operating Characteristic Curve on Test Set Performance of the Best, Middle, Worse, and Full Training Models.** For each of the 100 training cohort sets used had `r round(length(rownames(metaI))*0.8)` individuals and the testing cohort sets had `r round(length(rownames(good_metaf))*0.2)` individuals.  The AUC on the test sets for the best, middle, and worse models from training were `r format(model_test_AUC_summary["best", "AUC"], digits = 3)`, `r format(model_test_AUC_summary["middle", "AUC"], digits = 3)`, and `r format(model_test_AUC_summary["worse", "AUC"], digits = 3)`, respectively.  cvAUC is the 20 times repeated 10-fold cross-validated AUC from training.

**Figure 4: Breakdown by Carcinoma and Adenoma of Prediction Results for Initial and Follow Up***  A) Positive probability adjustment of those with carcinoma from intial to follow up sample  B) Positive probability adjustment of those with adenoma as well as those with SRN and the probability adjustment from initial to follow up sample.  The dotted line represents the threshold used to make the decision of whether a sample was lesion positive or not.

### 2016-12-07 submission/manuscript_outline_20161024.tex
Figure legend updates

\textbf{Figure 1: Change in Thetayc and Fit between initial and follow
up in adenoma or carcinoma group.} A) No significant difference was
found between the adenoma and carcinoma group for thetayc (P-value =
0.697). B) A significant difference was found between the adenoma and
carcinoma group for Fit (P-value = 2.15e-05).

@@

\textbf{Figure 3: Graph of the Receiver Operating Characteristic Curve
on Test Set Performance of the Best, Middle, and Worse Training Models.}
For each of the 100 training cohort sets used had 392 individuals and
the testing cohort sets had 13 individuals. The AUC on the test sets for
the best, middle, and worse models from training were 0.682, 0.815, and
0.931, respectively. cvAUC is the 10-fold cross-validated AUC from
training.

\textbf{Figure 4: Breakdown by Carcinoma and Adenoma of Prediction
Results for Initial and Follow Up}* A) Positive probability adjustment
of those with carcinoma from intial to follow up sample B) Positive
probability adjustment of those with adenoma as well as those with SRN
and the probability adjustment from initial to follow up sample. THe
dotted line represents the threshold used to make the decision of
whether a sample was lesion positive or not.

>>>>

\textbf{Figure 1: Change in Thetayc and Fit between initial and follow
up in adenoma or carcinoma group.} A) No significant difference was
found between the adenoma and carcinoma group for thetayc (P-value =
0.697). B) A significant difference was found between the adenoma and
carcinoma group for FIT (P-value = 2.15e-05).

@@

\textbf{Figure 3: Graph of the Receiver Operating Characteristic Curve
on Test Set Performance of the Best, Middle, Worse, and Full Training
Models.} For each of the 100 training cohort sets used had 392
individuals and the testing cohort sets had 13 individuals. The AUC on
the test sets for the best, middle, and worse models from training were
0.682, 0.815, and 0.931, respectively. cvAUC is the 20 times repeated
10-fold cross-validated AUC from training.

\textbf{Figure 4: Breakdown by Carcinoma and Adenoma of Prediction
Results for Initial and Follow Up}* A) Positive probability adjustment
of those with carcinoma from intial to follow up sample B) Positive
probability adjustment of those with adenoma as well as those with SRN
and the probability adjustment from initial to follow up sample. The
dotted line represents the threshold used to make the decision of
whether a sample was lesion positive or not.
